---
title: "Family complexity-287g Visuals"
author: "FE"
date: "May 23, 2018"
output: html_document
---

```{r setup, echo=FALSE, message=FALSE, cache=TRUE, warning=FALSE, cache.lazy = FALSE}
library(tidyverse)
library(haven)

setwd("U:/fc-deportation")

source("models_dd.r")
```

```{r packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(haven)

make_pred<-function(model){
  race<-unique(puma_long$race)
  fips<-4013
  state<-"4"
  years_to_active<- -3:5
  year<-2008
  c287_everactive<-TRUE
  newdat<-data.frame(expand.grid(race, fips, years_to_active, year, c287_everactive))
  names(newdat)<-c("race", "fips", "years_to_active", "year", "c287_everactive")
  ### make never implement scenario, everactive false, years_to_active==-1
  newdat_false<-expand.grid(race, fips, -1, 2008, FALSE)
  names(newdat_false)<-c("race", "fips", "years_to_active", "year", "c287_everactive")
  ### make df with rows equal to newdat
  newdat_false<-map_df(seq_len(length(years_to_active)), ~newdat_false)
  #### predict for each time group, for never implement
  predTRUE<-predict(model, newdat)
  predFALSE<-predict(model, newdat_false)
  predDIFF<-predTRUE-predFALSE
  newdatDIFF<-newdat
  newdatDIFF$pred<-predDIFF
  return(newdatDIFF)
}

```

#Family complexity models - PUMA population data

Below, I present model predictions from a series of models of family complexity outcomes as a function of 287g participation. Outcomes include:

- ckhhsize
- ckhhfams
- cpgkid         
- cpklivesmom    
- cpknolivespar  
- cpklivessinmom
- cpklivessinpar 
- cpknparhead    
- cpknfamhead    
- cpmixgen   

I describe the model specification at the beginning of each section. Outcome variables are labeled on the y axis of all plots. 

Counties that never implemented 287g have the year-to-287g variable set to a constant 0, and are included in the estimation of the 287g0yrs parameter

These models estimate the effect of 287g on all family complexity outcomes with state and year fixed effects and within-state trends. All PUMA counties are included in these models, regardless of 287g participation. 

The models take the form:

$$\textrm{E}(\sqrt{outcome_{it}}) \sim \alpha_i + \delta_j + \sum_{t=j}^{g}\theta_{j}X_{ij} + \varepsilon_{ij} $$

Alpha is a vector of county fixed effects, delta is a vector of event-relative time fixed effects (with non-implementing counties set to constant j= -1, j=0 is impementation year), X_ij is the interaction between ever-active and event-time.

# ALL CASES, NO TRENDS
```{r puma_all, echo=FALSE, message=FALSE, warning=FALSE}

######################################################
#### puma_models_1 by relative 287g implementation time
plot_out<-list()

for(i in 1:length(puma_models)){
  var<-puma_outcomes[i]
  newdatDIFF<-make_pred(puma_models[[i]])
  plot_out[[i]]<-ggplot(newdatDIFF,
         aes(x=years_to_active, y = pred))+
    geom_point()+
    geom_hline(yintercept=0, lty=2)+
    geom_vline(xintercept=0, lty=2)+
    facet_wrap(~race)+
    ylab(var)
}

plot_out[[1]]
plot_out[[2]]
plot_out[[3]]
plot_out[[4]]
plot_out[[5]]
plot_out[[6]]
plot_out[[7]]
plot_out[[8]]
plot_out[[9]]
plot_out[[10]]

```

# WITH COUNTY TRENDS, ALL CASES

These models add a county*year trend to the models

```{r puma_trends, echo=FALSE, message=FALSE, warning=FALSE}

######################################################
#### puma_models_1 by relative 287g implementation time
plot_out<-list()

for(i in 1:length(puma_models_trend)){
  var<-puma_outcomes[i]
  newdatDIFF<-make_pred(puma_models_trend[[i]])
  plot_out[[i]]<-ggplot(newdatDIFF,
         aes(x=years_to_active, y = pred))+
    geom_point()+
    geom_hline(yintercept=0, lty=2)+
    geom_vline(xintercept=0, lty=2)+
    facet_wrap(~race)+
    ylab(var)
}

plot_out[[1]]
plot_out[[2]]
plot_out[[3]]
plot_out[[4]]
plot_out[[5]]
plot_out[[6]]
plot_out[[7]]
plot_out[[8]]
plot_out[[9]]
plot_out[[10]]

```
