---
title: "Family complexity-287g Visuals"
author: "FE"
date: "May 23, 2018"
output: html_document
---

```{r setup, echo=FALSE, message=FALSE, cache=TRUE, warning=FALSE, cache.lazy = FALSE}
library(tidyverse)
library(haven)

setwd("U:/fc-deportation")

source("models_dd.r")
```

```{r packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(haven)

make_pred<-function(model){
  race<-unique(puma_long$race)
  fips<-4013
  state<-"4"
  years_to_active<- -4:6
  year<-2008
  c287_everactive<-TRUE
  newdat<-data.frame(expand.grid(race, fips, years_to_active, year, c287_everactive))
  names(newdat)<-c("race", "fips", "years_to_active", "year", "c287_everactive")
  ### make never implement scenario, everactive false, years_to_active==-1
  newdat_false<-expand.grid(race, fips, 0, 2008, FALSE)
  names(newdat_false)<-c("race", "fips", "years_to_active", "year", "c287_everactive")
  ### make df with rows equal to newdat
  newdat_false<-map_df(seq_len(length(years_to_active)), ~newdat_false)
  #### predict for each time group, for never implement
  predTRUE<-predict(model, newdat, interval = "confidence")
  predFALSE<-predict(model, newdat_false)
  predDIFF<-predTRUE-predFALSE
  newdatDIFF<-newdat
  newdatDIFF$pred<-predDIFF[,1]
  newdatDIFF$lwr<-predDIFF[,2]
  newdatDIFF$upr<-predDIFF[,3]
  
  return(newdatDIFF)
}

make_pred_new<-function(model, data){
  ### get all non- FE coefficients
  model_coefs<-as.data.frame(summary(model)$coefficients[,1:2])
  z<-c(grep("fips", row.names(model_coefs)), grep("\\(year\\)", row.names(model_coefs)))
  model_coefs<-model_coefs[-z,]
  betas<-data.frame(beta = model_coefs$Estimate)
  row.names(betas)<-row.names(model_coefs)
  ### replace with chosen robust se estimation method
  ### reduce vcov matrix to remove fixed effects
  vc<-vcov(model)
  z<-c(grep("fips", row.names(vc)), grep("\\(year\\)", row.names(vc)))
  vc<-vc[-z,-z]
  model_coefs[,2]<-sqrt(diag(vc))
  # make template for each scenario
  scen_temp<-rep(F, nrow(betas))
  names(scen_temp)<-row.names(model_coefs)
  scen_temp<-as.data.frame(t(scen_temp))
  years<-paste("factor(years_to_active)", -4:6, sep="")
  blk_scens<-list()
  # make year - 4 scen
  blk_scens[[1]]<-scen_temp%>%
    mutate(raceblack=TRUE)
  for(i in 2:(length(years))){
    yr<-years[i]
    blk_scens[[i]]<-scen_temp
    blk_scens[[i]][,"raceblack"]<-TRUE
    blk_scens[[i]][,yr]<-TRUE    
  }
  names(blk_scens)<-as.character(-4:6)
  
  blk_preds<-lapply(blk_scens, function(x){
   colSums(t(x) * betas)
  })
  #### white scenarios
  wht_yr<-paste("racewhite, nh:", years, sep="")
  wht_scens<-list()
  wht_scens[[1]]<-scen_temp%>%
    mutate('racewhite, nh'=TRUE)
  for(i in 2:(length(years))){
    yr<-years[i]
    wht_scens[[i]]<-scen_temp
    wht_scens[[i]][,"racewhite, nh"]<-TRUE
    wht_scens[[i]][,yr]<-TRUE    
    wht_scens[[i]][,wht_yr[i]]<-TRUE 
  }
  names(wht_scens)<-as.character(-4:6)
  
  wht_preds<-lapply(wht_scens, function(x){
   colSums(t(x) * betas)
  })
  
  #### hisp scenarios
  hisp_yr<-paste("racehispanic:", years, sep="")
  hisp_scens<-list()
  hisp_scens[[1]]<-scen_temp%>%
    mutate('racehispanic'=TRUE)
  ## standard error for model estimate of b1+b2 with new vcov matrix, replicates(predict)
  ## vc defined at top
  ## var_b1,b2 = var(b1) + var(b2) + 2cov(b1,b2)
  ## since reference (t=-4) is intercept only, e[y_-4 - y_0] = -b_0 - b_race0
  se_scens<-rep(NA, length(hisp_scens))
  index<-c(which(rownames(vc)==""), which(rownames(vc)==hisp_yr[1]))
    ## var_b1,b2 = var(b1) + var(b2) + 2cov(b1,b2)
  se_scens[1]<-sqrt(vc[index[1], index[1]] + 
                        vc[index[2], index[2]] + 
                        2 * vc[index[1], index[2]])
  for(i in 2:(length(years))){
    yr<-years[i]
    hisp_scens[[i]]<-scen_temp
    hisp_scens[[i]][,"racehispanic"]<-TRUE
    hisp_scens[[i]][,yr]<-TRUE    
    hisp_scens[[i]][,hisp_yr[i]]<-TRUE 
    index<-c(which(rownames(vc)==yr), which(rownames(vc)==hisp_yr[i]))
    ## var_b1,b2 = var(b1) + var(b2) + 2cov(b1,b2)
    se_scens[i]<-sqrt(vc[index[1], index[1]] + 
                        vc[index[2], index[2]] + 
                        2 * vc[index[1], index[2]])
  }
  names(hisp_scens)<-as.character(-4:6)
  
  hisp_preds<-lapply(hisp_scens, function(x){
   colSums(t(x) * betas)
  })

  make_diffs<-function(x){
    output<-data.frame("beta" = rep(NA, length(x)), 
                       "lower" = rep(NA, length(x)), 
                       "upper" = rep(NA, length(x)))
    for(i in 1:length(x)){
      output[i, ]<-x[[i]]-x[["0"]]["beta"]
    }
    output$years_to_active<--4:6
    return(output)
  }
  
  preds_out<-make_diffs(hisp_preds)
  preds_out$race<-"hispanic"
  preds_temp<-make_diffs(blk_preds)
  preds_temp$race<-"black"
  preds_out<-rbind(preds_out, preds_temp)
  preds_temp<-make_diffs(wht_preds)
  preds_temp$race<-"white, nh"
  preds_out<-rbind(preds_out, preds_temp)
  
}

x<-model
clcov<-vcov(x)
newdata<-hisp_scens[[10]]
newdata$fips<-"4013"
newdata$year<-"2008"


###uncertainty for race==hispanic, et==1, 

vc<-vcov(model)
se<-sqrt(diag(vc)["factor(years_to_active)1"] + diag(vc)["racehispanic:factor(years_to_active)1"])

```

#Family complexity models - PUMA population data

Below, I present model predictions from a series of models of family complexity outcomes as a function of 287g participation. Outcomes include:

- ckhhsize
- ckhhfams
- cpgkid         
- cpklivesmom    
- cpknolivespar  
- cpklivessinmom
- cpklivessinpar 
- cpknparhead    
- cpknfamhead    
- cpmixgen   

I describe the model specification at the beginning of each section. Outcome variables are labeled on the y axis of all plots. 

Counties that never implemented 287g have the year-to-287g variable set to a constant 0, and are included in the estimation of the 287g0yrs parameter

These models estimate the effect of 287g on all family complexity outcomes with state and year fixed effects and within-state trends. All PUMA counties are included in these models, regardless of 287g participation. 

The models take the form:

$$\textrm{E}(\sqrt{outcome_{it}}) \sim \alpha_i + \delta_j + \sum_{t=j}^{g}\theta_{j}X_{ij} + \varepsilon_{ij} $$

Alpha is a vector of county fixed effects, delta is a vector of event-relative time fixed effects (with non-implementing counties set to constant j= -1, j=0 is impementation year), X_ij is the interaction between ever-active and event-time.

# ALL CASES, NO TRENDS
```{r puma_all, echo=FALSE, message=FALSE, warning=FALSE}

######################################################
#### puma_models_1 by relative 287g implementation time
plot_out<-list()

model<-test
data<-test_dat

for(i in 1:length(puma_models)){
  var<-puma_outcomes[i]
  newdatDIFF<-make_pred(model)
  plot_out_test[[i]]<-ggplot(newdatDIFF,
         aes(x=years_to_active, y = pred))+
    geom_point()+
    geom_errorbar(aes(ymax=upr, ymin=lwr))+
    geom_hline(yintercept=0, lty=2)+
    geom_vline(xintercept=0, lty=2)+
    facet_wrap(~race)
  
}


plot_out[[1]]
plot_out[[2]]
plot_out[[3]]
plot_out[[4]]
plot_out[[5]]
plot_out[[6]]
plot_out[[7]]
plot_out[[8]]
plot_out[[9]]
plot_out[[10]]

```

# WITH COUNTY TRENDS, ALL CASES

These models add a county*year trend to the models

```{r puma_trends, echo=FALSE, message=FALSE, warning=FALSE}

######################################################
#### puma_models_1 by relative 287g implementation time
plot_out<-list()

for(i in 1:length(puma_models_trend)){
  var<-puma_outcomes[i]
  newdatDIFF<-make_pred(puma_models_trend[[i]])
  plot_out[[i]]<-ggplot(newdatDIFF,
         aes(x=years_to_active, y = pred))+
    geom_point()+
    geom_hline(yintercept=0, lty=2)+
    geom_vline(xintercept=0, lty=2)+
    facet_wrap(~race)+
    ylab(var)
}

plot_out[[1]]
plot_out[[2]]
plot_out[[3]]
plot_out[[4]]
plot_out[[5]]
plot_out[[6]]
plot_out[[7]]
plot_out[[8]]
plot_out[[9]]
plot_out[[10]]

```
