---
title: "Family complexity-287g Visuals"
author: "FE"
date: "May 23, 2018"
output: html_document
---

```{r setup, echo=FALSE, message=FALSE, cache=TRUE, warning=FALSE, cache.lazy = FALSE}
library(tidyverse)
library(haven)

setwd("U:/fc-deportation")

source("models_dd.r")
```

```{r packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(sandwich)

make_marg_eff<-function(model, data){
  ### get all non- FE coefficients
  model_coefs<-as.data.frame(summary(model)$coefficients[,1:2])
  z<-c(grep("fips", row.names(model_coefs)), grep("\\(year\\)", row.names(model_coefs)))
  model_coefs<-model_coefs[-z,]
  betas<-data.frame(beta = model_coefs$Estimate)
  row.names(betas)<-row.names(model_coefs)
  
  ### replace with chosen robust se estimation method
  ### reduce vcov matrix to remove fixed effects
  vc<-vcov(model)### ADD ROBUST VCOV ESTIMATION HERE
  
  z<-c(grep("fips", row.names(vc)), grep("\\(year\\)", row.names(vc)))
  vc<-vc[-z,-z]
  model_coefs[,2]<-sqrt(diag(vc))
  
    ### expected marginal effect is t_n - t_0, CI is 2*SE  
  blk_est<-model_coefs[grep("black", row.names(model_coefs)),]
  blk_est[,1]<-blk_est[,1]-blk_est[1,1]
  
  wht_est<-model_coefs[grep("white", row.names(model_coefs)),]
  wht_est[,1]<-wht_est[,1]-wht_est[1,1]
  
  hisp_est<-model_coefs[grep("hispanic", row.names(model_coefs)),]
  hisp_est[,1]<-hisp_est[,1]-hisp_est[1,1]
  
  ### bind, send out
  blk_est<-blk_est%>%
    mutate(race="Black",
           years_to_active = c(0, -4:-1, 1:6))%>%
    rename(diff_est = Estimate,
           se = "Std. Error")
  
  wht_est<-wht_est%>%
    mutate(race="White",
           years_to_active = c(0, -4:-1, 1:6))%>%
    rename(diff_est = Estimate,
           se = "Std. Error")
  
  hisp_est<-hisp_est%>%
    mutate(race="Hispanic",
           years_to_active = c(0, -4:-1, 1:6))%>%
    rename(diff_est = Estimate,
           se = "Std. Error")
  
  diff_est<-bind_rows(blk_est, wht_est, hisp_est)
  
  return(diff_est)
}

### for each model

```

#Family complexity models - PUMA population data

Below, I present model predictions from a series of models of family complexity outcomes as a function of 287g participation. Outcomes include:

- ckhhsize
- ckhhfams
- cpgkid         
- cpklivesmom    
- cpknolivespar  
- cpklivessinmom
- cpklivessinpar 
- cpknparhead    
- cpknfamhead    
- cpmixgen   

I describe the model specification at the beginning of each section. Outcome variables are labeled on the y axis of all plots. 

Counties that never implemented 287g have the year-to-287g variable set to a constant 0, and are included in the estimation of the 287g0yrs parameter

These models estimate the effect of 287g on all family complexity outcomes with state and year fixed effects and within-state trends. All PUMA counties are included in these models, regardless of 287g participation. 

The models take the form:

$$\textrm{E}(\sqrt{outcome_{it}}) \sim \alpha_i + \delta_j + \sum_{t=j}^{g}\theta_{j}X_{ij} + \varepsilon_{ij} $$

Alpha is a vector of county fixed effects, delta is a vector of event-relative time fixed effects (with non-implementing counties set to constant j= -1, j=0 is impementation year), X_ij is the interaction between ever-active and event-time.

#STANDARD ERRORS

Compare robust SE methods below. Note that CL-FIPS-YR-RACE std. errors are consistent with standard errors from comparable RE models.

```{r}
# test<-puma_models[[3]]
# test_dat<-puma_model_data[[3]]
vc<-list("standard" = vcov(test),
         "sandwich" = sandwich(test),
         "hc1" = vcovHC(test),
         "CL-FIPS" = vcovCL(test, cluster = test_dat[, c("fips")], type = "HC1", fix=TRUE),
         "CL-FIPS-YR" = vcovCL(test, cluster = test_dat[, c("fips", "year")], type = "HC1", fix=TRUE),
         "CL-FIPS-YR-RACE" = vcovCL(test, cluster = test_dat[, c("fips", "year", "race")], type = "HC1", fix=TRUE))
         #"HC" = vcovHC(test, type="HC1"))

se<-function(vcov)sapply(vcov, function(x)round(sqrt(diag(x)),3))
se(vc)[1:20,]

```

# ALL CASES, NO TRENDS
```{r puma_all, echo=FALSE, message=FALSE, warning=FALSE}

######################################################
#### puma_models_1 by relative 287g implementation time
plot_out<-list()

for(i in 1:length(puma_models)){
  var<-puma_outcomes[i]
  newdatDIFF<-make_marg_eff(model, data)
  plot_out_test[[i]]<-ggplot(newdatDIFF,
         aes(x=years_to_active, y = diff_est))+
    geom_point()+
    geom_errorbar(aes(ymax = diff_est + 1.96*se, 
                      ymin=diff_est - 1.96*se))+
    geom_hline(yintercept=0, lty=2)+
    geom_vline(xintercept=0, lty=2)+
    facet_wrap(~race)
  
}


plot_out[[1]]
plot_out[[2]]
plot_out[[3]]
plot_out[[4]]
plot_out[[5]]
plot_out[[6]]
plot_out[[7]]
plot_out[[8]]
plot_out[[9]]
plot_out[[10]]

```

# WITH COUNTY TRENDS, ALL CASES

These models add a county*year trend to the models

```{r puma_trends, echo=FALSE, message=FALSE, warning=FALSE}

######################################################
#### puma_models_1 by relative 287g implementation time
plot_out<-list()

for(i in 1:length(puma_models_trend)){
  model<-puma_models_trend[[i]]
  var<-puma_outcomes[i]
  newdatDIFF<-make_marg_eff(model, data)
  plot_out_test[[i]]<-ggplot(newdatDIFF,
         aes(x=years_to_active, y = diff_est))+
    geom_point()+
    geom_errorbar(aes(ymax = diff_est + 1.96*se, 
                      ymin=diff_est - 1.96*se))+
    geom_hline(yintercept=0, lty=2)+
    geom_vline(xintercept=0, lty=2)+
    facet_wrap(~race)
}

plot_out[[1]]
plot_out[[2]]
plot_out[[3]]
plot_out[[4]]
plot_out[[5]]
plot_out[[6]]
plot_out[[7]]
plot_out[[8]]
plot_out[[9]]
plot_out[[10]]

```
